Estimating Life-Stage Specific Habitat Capacity for Anadromous Salmonids using Quantile Random Forest Models

### 2020-01-28 analysis/paper/paper.Rmd
added a note to remember to add more to the abstract, and a comment to think about in the conclusions.

---
title: "Estimating Life-Stage Specific Habitat Capacity for Anadromous Salmonids using Quantile Random Forest Models"
author:
  - Kevin E. See:
      email: Kevin.See@biomark.com
      institute: [biomark]
      correspondence: true
  - Michael W. Ackerman:
      email: Mike.Ackerman@biomark.com
      institute: [biomark]
      correspondence: false
  - Richard A. Carmichael:
      email: Richie.Carmichael@biomark.com
      institute: [biomark]
      correspondence: false
  - Sarah Hoffman:
      email: Sarah.Hoffman@biomark.com
      institute: [biomark]
      correspondence: false
  - Chris Beasley:
      email: Chris.Beasley@biomark.com
      institute: [biomark]
      correspondence: false
institute:
  - biomark: Biomark, Inc. 705 South 8th St., Boise, Idaho, 83702, USA
date: "`r format(Sys.time(), '%B %d, %Y')`"
output: 
    bookdown::html_document2:
      fig_caption: yes
      pandoc_args:
      - --lua-filter=../templates/scholarly-metadata.lua
      - --lua-filter=../templates/author-info-blocks.lua
      - --lua-filter=../templates/pagebreak.lua
    bookdown::pdf_document2:
      fig_caption: yes
      pandoc_args:
      - --lua-filter=../templates/scholarly-metadata.lua
      - --lua-filter=../templates/author-info-blocks.lua
      - --lua-filter=../templates/pagebreak.lua
    bookdown::word_document2:
      fig_caption: yes
      reference_docx: "../templates/template.docx" # Insert path for the DOCX file
      pandoc_args:
      - --lua-filter=../templates/scholarly-metadata.lua
      - --lua-filter=../templates/author-info-blocks2.lua
      - --lua-filter=../templates/pagebreak.lua
bibliography:
# - /Users/seek/OneDrive - Merck Sharp & Dohme, Corp/Bibliography/Research.bib
# - /Users/seek/OneDrive - Merck Sharp & Dohme, Corp/Bibliography/SoftwareCitations.bib
- references.bib
- packages.bib
csl: "../templates/ecological-applications.csl" # Insert path for the bib-style
abstract: |
  The QRF model presented here provided estimates of habitat carrying capacity for Chinook salmon parr during the summer months, at both the site and watershed scale. Total capacity estimates for watersheds closely matched estimates from alternative fish productivity models. Carrying capacity estimates based on QRF, like those presented here, provide managers a framework to guide the identification, prioritization, and development of habitat rehabilitation actions to recover salmon populations. 
keywords: |
  carrying capacity; quantile regression; random forests; Chinook; quantile regression forest
highlights: |
  These are the highlights. 
---

@@

>>>>

---
title: "Estimating Life-Stage Specific Habitat Capacity for Anadromous Salmonids using Quantile Random Forest Models"
author:
  - Kevin E. See:
      email: Kevin.See@biomark.com
      institute: [biomark]
      correspondence: true
  - Michael W. Ackerman:
      email: Mike.Ackerman@biomark.com
      institute: [biomark]
      correspondence: false
  - Richard A. Carmichael:
      email: Richie.Carmichael@biomark.com
      institute: [biomark]
      correspondence: false
  - Sarah Hoffman:
      email: Sarah.Hoffman@biomark.com
      institute: [biomark]
      correspondence: false
  - Chris Beasley:
      email: Chris.Beasley@biomark.com
      institute: [biomark]
      correspondence: false
institute:
  - biomark: Biomark, Inc. 705 South 8th St., Boise, Idaho, 83702, USA
date: "`r format(Sys.time(), '%B %d, %Y')`"
output: 
    bookdown::html_document2:
      fig_caption: yes
      pandoc_args:
      - --lua-filter=../templates/scholarly-metadata.lua
      - --lua-filter=../templates/author-info-blocks.lua
      - --lua-filter=../templates/pagebreak.lua
    bookdown::pdf_document2:
      fig_caption: yes
      pandoc_args:
      - --lua-filter=../templates/scholarly-metadata.lua
      - --lua-filter=../templates/author-info-blocks.lua
      - --lua-filter=../templates/pagebreak.lua
    bookdown::word_document2:
      fig_caption: yes
      reference_docx: "../templates/template.docx" # Insert path for the DOCX file
      pandoc_args:
      - --lua-filter=../templates/scholarly-metadata.lua
      - --lua-filter=../templates/author-info-blocks2.lua
      - --lua-filter=../templates/pagebreak.lua
bibliography:
# - /Users/seek/OneDrive - Merck Sharp & Dohme, Corp/Bibliography/Research.bib
# - /Users/seek/OneDrive - Merck Sharp & Dohme, Corp/Bibliography/SoftwareCitations.bib
- references.bib
- packages.bib
csl: "../templates/ecological-applications.csl" # Insert path for the bib-style
abstract: |
  Needs more...

  The QRF model presented here provided estimates of habitat carrying capacity for Chinook salmon parr during the summer months, at both the site and watershed scale. Total capacity estimates for watersheds closely matched estimates from alternative fish productivity models. Carrying capacity estimates based on QRF, like those presented here, provide managers a framework to guide the identification, prioritization, and development of habitat rehabilitation actions to recover salmon populations. 
keywords: |
  carrying capacity; quantile regression; random forests; Chinook; quantile regression forest
highlights: |
  These are the highlights. 
---

@@

<!-- Consider pulling back and thinking about whether these kinds of techniques could be applied to other systems (terrestial, ocean, etc.). If not, we may want to target a more fisheries-centric journal -->
